Resource-use and the Value-Productivity Tradeoff in Australian Winegrowing Regions

### 2023-07-06 article.tex
aaahhhh why didnt you commit any of these changes this weekgit add --all!

    \title{Resource Use and the Value-Productivity Tradeoff in Australian Winegrowing Regions}

@@

\section{Introduction}
The global focus on sustainability in agronomic industries has changed the way in which these enterprises do business. When strategies for a sustainable winegrowing industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant yield verses quality produced. This dilemma exists across agriculture within shared fundamental considerations such as water and nitrogen inputs \citep{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}. Within viticulture (the cultivation of grapes for wine production) quality is driven by its integration within the wine industry; with a wine's potential quality being initially defined through the chemical makeup of the grapes used in its production. The consideration of sustainability is further complicated by environmental and socio-demographic pressures. In the Australian context, these include biosecurity, climate and international market demands.
\newline
In this analysis we observe relationships between yield and quality through the use of linear models. Quality can be defined in a variety of ways, for example analysing grapes' aroma, chemical composition and color. For the purpose of this study, quality was defined by winegrape crops' financial value per tonne. This definition assumes due diligence on the side of those that purchased the grapes; where market value of grapes heavily relies on grape quality \citep{yeggeInfluenceSensoryNonsensory2001}. Wine Australia also links grape quality to price per tonne, by explicitly defining grape quality within discrete price brackets.
\newline
An extensive amount of research into a variety of factors' effect on grape quality and yield exists.
% there needs to be references if there is extensive research
Due to the lack of long-term and in-depth data, individual effects are often studied in isolation \citep{abbalDecisionSupportSystem2016}. The lack of consolidated datasets also restricts the ability to gain statistical insights at large scales and across multiple regions \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data collected for the past 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions.
\newline
We aim to use this broad dataset to confirm the existence of a yield verse quality trade off within Australian winegrowing; one not prior confirmed explicitly across such extensive diversities.
% you require a reference here
In achieving this, the context of how resource use relates to yield and quality will also be described. We link these relations to the potential for improvement through decision-making processes, and highlight that the way moving forward will require the optimisation of this process. The practical addition of these aims is a baseline for comparison - given a vineyard within Australia, one could extrapolate their comparative efficiency with regard to the tradeoff between invested resources, yield and quality.
\section{Methods}
We created four linear models to explore relationships between resources used and vineyard outputs (see Table 1). The response variables of the models were yield and quality, with yield being measured in tonnes and quality being the product of yield and the average sale price per tonne. Both response variables were examined as totals and as scales of area harvested. Values were compared in this manner to observe how economies of scale affect the use of resources.

@@

\subsection{Data}
Data used in this analysis was sampled by Sustainable Winegrowing Australia and Wine Australia. Sustainable Winegrowing Australia is Australia's national wine industry sustainability program, which aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Wine Australia is an Australian Government statutory authority governed by the Wine Australia Act 2013 \citep{WineAustraliaAct2019}. 
\newline
Data sampled by Wine Australia included: summary statistics such as yield and average price of sale per tonne, for contexts such as region and grape varietal; this data was collected via phone surveys. Data recorded by Sustainable Winegrowing Australia was entered manually by winegrowers using a web based interface with some fields being optional, variables included: region, harvest year, yield, area harvested, water used and fuel used (diesel, petrol, biodiesel and LPG). To enable comparisons, total fuel was converted to tonnes of Carbon Dioxide equivalent. Two subsets of Sustainable Winegrowing Australia's data were defined. One subset contained all vineyards. The other subset contained vineyards which either recorded a value for average price of sale per tonne or had a regional value recorded by Wine Australia.
\newline
The first subset of data was used for Model 1 and Model 2 (see Table 1). This subset contained 5298 samples spanning the period from 2012 to 2022, covering 57 GI Regions and 1432 separate vineyards.
\newline
The second subset of data, was limited to vineyards that recorded a value for their average sale price of grapes per tonne. This subset was used for Model 3 and Model 4 (see Table 1); and contained 2878 samples spanning the period from 2015 to 2022, covering 51 GI Regions and 944 separate vineyards. 1842 of the values for average price of sale per tonne were extracted from Wine Australia surveys with the remaining 1036 being from Sustainable Winegrowing Australia's dataset.
\newline
Data used in each model was limited to samples that had recorded values for the variables used (see Table 1). After reviewing correlation coefficients the data was logarithmically transformed, centred and scaled by standard deviation. Two values for average sale price were removed from the dataset, due to a recording of \$1. 
% \citep{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2012,winemakersfederationofaustraliaNationalVintageReport2013,winemakersfederationofaustraliaNationalVintageReport2014,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018}.
Other variables including the use of renewable energy, contractors; and pressures such as frost, fire and disease were also explored. Variables that did not significantly contribute to the prediction of a response variable were excluded.

\subsection{Total Emissions}
The equation given from the Australian National Greenhouse Accounts Factors, shown as

\begin{equation}
\label{(1)}
    tCO_{2}e={{Q \times EC \times EF1 + EF3}\over{1000}},
\end{equation}

was used to convert the quantity of fuel in litres, $Q$, using a prescribed Energy Content, $EC$, and emission factors of scope one, $EF1$, and scope three, $EF3$, to tonnes of Carbon Dioxide equivalent, $tCO2e$ \citep{departmentofclimatechangeenergytheenvironmentandwaterAustralianNationalGreenhouse2022}. Emissions were calculated for total diesel, petrol, bio-diesel and LPG used.

% What the hell is the below paragraph and why is it here?
%The variables were reviewed for correlations by using a Pearson's Correlation Coefficient (see Tables 1, 2 and 3). This was undertaken for data on the original scale (see Table 1) and for data as a logarithmic transform (see Table 2). All P-values were found to be significant (< 2.200E-16), except the non-transformed values for water used (see Table 3). The logarithmic transforms performed the best due to a skew likely caused by a greater number of smaller vineyards within the dataset (see Table 4).

\subsection{Region}
Differences in vineyard locations were captured through the use of Geographical Indicator Regions (GI Regions). Each GI Region has its own unique mixture of climatic and geophsical properties that describes a unique winegrowing region within Australia; these regions were predefined by Wine Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}.

The site of a vineyard predetermines several physical parameters such as climate, geology and soil; making location a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. The climatic properties of each GI Region were summarised by using predefined climatic classifications as per the \citet{swaSustainableWinegrowingAustralia2021} user manual. The user manual describes climates by rainfall and temperature, creating supersets of Regions of similar climatic properties. The climatic groups were used to illustrate similarities and differences occurring in areas larger than GI regions.

\subsection{Analysis}
General Linear Models were used as they offered the ability to produce statistical models that were explicit in the relationships between predictors and response variables. They also allowed the exploration of interactions between predictors and easily comparable differences in the influence and magnitude of relationships.

Data preprocessing, such as logarithmic transforms, was done using the Python programming language \citep{g.vanrossumPythonTutorialTechnical1995}. Linear models were created using the R statistical programming language \citep{rcoreteamLanguageEnvironmentStatistical2021}. These models were created iteratively to explore a variety of variable interactions and approaches to modelling the data. Not all explored approaches yielded improvements or accurate models. Alternate approaches included the use of Splines, hierarchical regression, Additive and Generalised Linear Models. Other variables were also explored but not used due to low reporting values such as fertiliser, tractor and contractor use. The use of only scope one emissions was due to the same reason where scope 2 sources were recorded sporadically at best.

\subsection{Model Validation}
Models were validated using K-fold cross validation calculated through the R Caret Package \citep{kuhnBuildingPredictiveModels2008}. K-fold cross validation works by removing a subset of data from the sample used to train models and then predicts those variables to determine how sensitive the model is to changes in the sample data. For this analysis each model was validated using 10 folds, repeated 100 times. % A reference for this is absolutely needed.

\section{Results}
\subsection{Exploratory Analysis}
Simple linear relationships between variables were explored using Pearson Correlation Coefficients. This was undertaken for data on the original scale (see Table 2) and for data as a logarithmic transform (see Table 3). Strong relationships were found to be present, as all P-values were considered significant (< 2.200E-16, see Tables 2 and 3), except for the non-transformed values for water used (see Table 4). The logarithmic transforms showed the strongest correlations, this was likely due to a skew caused by a greater number of smaller vineyards within the dataset (see Table 5).

@@

\subsection{General Linear Models}
Models 1 and 2 showed significant relationships between each of the predictors and their response variable (see Tables 6 and 7). Variables in models 3 and 4 reported similar significance; except for scope 1 emissions (see Tables 8 and 9). Scope one emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values. Even though not significant within models 3 and 4, when using the Pearson Correlation Coefficients, scope one emissions was strongly correlated to every Model's response variable; this was especially so for Model 1 and 4 (Yeild and average price per tonne as a ratio to area harvested, respectively).

@@

The issue of model 1 and 2 over predicting yield, may have been due to preventative measures brought on by regional pressures such as fire, frost and disease. Where, more resources were required to prevent these issues from spreading within a region, thus disproportionately effecting some vineyards compared to others locally. This type of maintenance is not well captured especially when considering that some regions, those in warmer areas are not as prone to disease as cooler climates and could potentially have lower operating costs per hectare. This could create a discrepancy in vineyards that utilise preventative measures in wetter regions, as opposed to those who do not, and thus expend less fuel and energy but risk disease. When reviewing the differences between regions it is important to consider that vineyards in Hot Very Dry areas can be hundreds of times the size of those in other regions. It is interesting that while area, although significantly correlated to the ratio of yield to area, was still lower than water and about the same as emissions. This points to economies of scale playing a role but still being only one consideration alongside the potential resources that can be used. The negative trend between size and average sales price could also be a side effect of mass supply verse demand, especially when looking at the level of difference in production of some vineyards (see Table 4). The relationships between yield, value and area are not simply about efficiently producing the most grapes; sales price and by association grape quality, are integral to the profitability, and this is strongly linked to resource use and thus the longevity and sustainability of a vineyard.

>>>>

    \title{Resource-use and the Value-Productivity Tradeoff in Australian Winegrowing Regions}

@@

\section{Introduction}
The global focus on sustainability in agronomic industries has changed the way in which these enterprises do business. When strategies for a sustainable winegrowing industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant yield verses quality produced. This dilemma exists across agriculture through shared fundamental considerations such as water use and nitrogen levels \citep{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}. Quality in viticulture (the cultivation of grapes for wine production) is driven through its integration within the wine industry; with a wine's potential quality being initially defined through the chemical makeup of the grapes used in its production. The consideration of sustainability within viticulture is further complicated by environmental and socio-demographic pressures. In the Australian context, these include: biosecurity, climate and international market demands.
\newline
In this analysis we observe relationships between yield and quality through the use of linear models. Although an extensive amount of research into a variety of factors' effect on grape quality and yield exists; due to the lack of long-term and in-depth data, individual effects are often studied in isolation \citep{abbalDecisionSupportSystem2016}. The lack of consolidated datasets also restricts the ability to gain statistical insights at large scales and across multiple regions \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data collected for the past 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions.
\newline
We aim to use this broad dataset to confirm the existence of a yield verse quality trade off within Australian winegrowing; one not prior confirmed explicitly across such extensive diversities.
% you require a reference here
In achieving this, the context of how resource-use relates to yield and quality will also be described. We link these relations to the potential for improvement through decision-making processes, whilst highlighting that the way moving forward will require the optimisation of these processes. The practical addition of these aims is a baseline for comparison - given a vineyard within Australia, one could extrapolate their comparative efficiency with regard to the tradeoff between invested resources, yield and quality.
\section{Methods}
We created four linear models to explore relationships between resource-use and vineyard outputs (see Table 1). The data was sourced from Sustainable Winegrowing Australia and Wine Australia. Variables used included: yield, average sale price, region, water use, emissions, area harvested and year. After fitting to the data, each model was validated using k-fold cross validation.

@@

\subsection{Analysis}
Before models were fit to the data, Pearson Correlation Coefficients were used to look at the existence of linear relationships between predictor variables. These relationships were summarised in correlation matrices to compare levels of interaction present between predictor variables. The relationships between the predictors and response variables were then modelled using General Linear Models. Both the Pearson Correlation Coefficients and General Linear Models were created using the R statistical programming language \citep{rcoreteamLanguageEnvironmentStatistical2021}. General Linear Models were chosen as they offer the ability to produce statistical models that are explicit in the relationships between predictors and response variables.
%reference?
General Linear Models also allow the exploration of interactions between predictors and easily comparable differences in the influence and magnitude of relationships.
% reference?
 A variety of alternate methods to General Linear Models was also explored, including: Splines, hierarchical regression, Additive and Generalised Linear Models. These alternative approaches were not used as final models due to offering no further improvements or to producing inaccurate models. 
\newline
The response variables of the models were yield and quality. The definition of quality was an important consideration, as quality can be defined in a variety of ways, for example analysing grapes': aroma, chemical composition and color. For the purpose of this study, quality was defined by the financial value of winegrape crops' average sale price per tonne. This definition was used due to the market value of winegrapes being reliant on grape quality and because Wine Australia explicitly defines grape quality through the use of discrete price brackets in their annual reports
% We need a reference to where they did this
% Did they do this more prolifically at some point as well?
; the generalisation made to reflect quality through using average price assumed a due diligence of those who purchased the grapes \citep{yeggeInfluenceSensoryNonsensory2001}. Yield was defined as the total tonnes of grapes harvested. Both response variables were examined as totals and as scales of area harvested. Values were compared in this manner to observe how economies of scale affect the use of resources.
\subsection{Data}
Data used in this analysis was sampled by Sustainable Winegrowing Australia and Wine Australia. Sustainable Winegrowing Australia is Australia's national wine industry sustainability program, which aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Wine Australia is an Australian Government statutory authority governed by the Wine Australia Act 2013 \citep{WineAustraliaAct2019}.
\newline
Data sampled by Wine Australia was collected via phone surveys and included: summary statistics such as yield and average price of sale per tonne; these values were summarised by region and grape varietal. Data recorded by Sustainable Winegrowing Australia was entered manually by winegrowers using a web based interface with some fields being optional, variables included: region, harvest year, yield, area harvested, water used and fuel used (diesel, petrol, biodiesel and LPG). To enable direct comparisons between fuels, they were converted to tonnes of Carbon Dioxide equivalent. 
\newline
The inclusion of Wine Australia data was due to average sale price being an optional field in Sustainable Winegrowing Australia's dataset. 
Regional average prices from Wine Australia were filled into values that were missing from the Sustainable Winegrowing Australia data; the common practice of purchasing grapes at regional prices was an important consideration in this decision.
%{It would be lovely to have a reference for this but it is currently only anacdotal.}
Two subsets of data were then created for the analysis. The first subset contained all vineyards and was used for Models 1 and 3. The second subset contained vineyards which either recorded a value for average price of sale per tonne through Sustainable Winegrowing Australia, or were within a region with an average price of sale recorded by Wine Australia; this subset was used for Models 2 and 4. These subsets meant that the data would be limited to samples which had recorded values for the response variables (see Table 1), where every sample had a recorded value for yield but not average price of sale per tonne.
\newline
The first subset of data was used for Model 1 and Model 2 (see Table 1). This subset contained 5298 samples spanning the period from 2012 to 2022, covering 57 GI Regions and 1432 separate vineyards.
\newline
The second subset of data, was limited to vineyards that recorded a value for their average sale price of grapes per tonne. This subset was used for Model 3 and Model 4 (see Table 1); and contained 2878 samples spanning the period from 2015 to 2022, covering 51 GI Regions and 944 separate vineyards. 1842 of the values for average price of sale per tonne were extracted from Wine Australia surveys with the remaining 1036 being from Sustainable Winegrowing Australia's dataset.
\newline
Additional variables were considered for analysis but were excluded due to being either underreported or had insignificant contributions to model accuracies. Variables explored but not used due to low reporting values included: fertiliser, tractor and contractor use, and scope 2 emissions. Variables considered but ultimately removed due to a lack of significant contributions to models, included: the use of renewable energy, contractors, and pressures such as frost, fire and disease.
\newline
Data preprocessing was conducted prior to analysis using the Python programming language \citep{g.vanrossumPythonTutorialTechnical1995}. Preprocessing included logarithmic transformations, centring and scaling by standard deviation. Variables such as scope 1, which required prior calculations were also computed using Python.
% Two values for average sale price were removed from the dataset, due to a recording of \$1. 
% \citep{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2012,winemakersfederationofaustraliaNationalVintageReport2013,winemakersfederationofaustraliaNationalVintageReport2014,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018}.

\subsection{Total Emissions}
The equation given from the Australian National Greenhouse Accounts Factors, shown as
\newline
\begin{equation}
\label{(1)}
    tCO_{2}e={{Q \times EC \times EF1 + EF3}\over{1000}},
\end{equation}
\newline
was used to convert the quantity of fuel in litres, $Q$, using a prescribed Energy Content, $EC$, and emission factors of scope one, $EF1$, and scope three, $EF3$, to tonnes of Carbon Dioxide equivalent, $tCO2e$ \citep{departmentofclimatechangeenergytheenvironmentandwaterAustralianNationalGreenhouse2022}. Emissions were calculated for total diesel, petrol, bio-diesel and LPG used. 
%\newline
% What the hell is the below paragraph and why is it here?
%The variables were reviewed for correlations by using a Pearson's Correlation Coefficient (see Tables 1, 2 and 3). This was undertaken for data on the original scale (see Table 1) and for data as a logarithmic transform (see Table 2). All P-values were found to be significant (< 2.200E-16), except the non-transformed values for water used (see Table 3). The logarithmic transforms performed the best due to a skew likely caused by a greater number of smaller vineyards within the dataset (see Table 4).
\subsection{Region}
Differences in vineyard locations were captured through the use of Geographical Indicator Regions (GI Regions). Each GI Region has its own unique mixture of climatic and geophysical properties that describes a unique winegrowing region within Australia; these regions were predefined by Wine Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Both Wine Australia and Sustainable Winegrowing Australia used the same GI Region format to describe location.
\newline
The site of a vineyard predetermines several physical parameters such as climate, geology and soil; making location a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. The climatic properties of each GI Region were summarised by using predefined classifications as per the \citet{swaSustainableWinegrowingAustralia2021} user manual. The user manual describes climates by rainfall and temperature, creating supersets of Regions of similar climatic properties. The climatic groups were used to illustrate similarities and differences occurring in areas larger than GI Regions.
\newline
\subsection{Model Validation}
Models were validated using K-fold cross validation calculated through the R Caret Package \citep{kuhnBuildingPredictiveModels2008}. K-fold cross validation works by removing a subset of data from the sample used to train models and then predicts those variables to determine how sensitive the model is to changes in the sample data. For this analysis each model was validated using 10 folds, repeated 100 times. % A reference for this is absolutely needed.

\section{Results}
\subsection{Exploratory Analysis}
Linear relationships between variables were explored using Pearson Correlation Coefficients. Values for these coefficients range between -1 and 1, and are indicative of . This was undertaken for data on the original scale (see Table 2) and for data as a logarithmic transform (see Table 3). Strong relationships were found to be present, as all P-values were considered significant (< 2.200E-16, see Tables 2 and 3), except for the non-transformed values for water used (see Table 4). The logarithmic transforms showed the strongest correlations, this was likely due to a skew caused by a greater number of smaller vineyards within the dataset (see Table 5).

@@

\subsection{General Linear Models}
Models 1 and 2 showed significant relationships between each of the predictors and their response variables (see Tables 6 and 7). Variables in models 3 and 4 reported similar significance; except for scope 1 emissions (see Tables 8 and 9). Scope one emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values. Even though not significant within models 3 and 4, when using the Pearson Correlation Coefficients, scope one emissions was strongly correlated to every Model's response variable; this was especially so for Model 1 and 4 (Yeild and average price per tonne as a ratio to area harvested, respectively).

@@

The issue of model 1 and 2 over predicting yield, may have been due to preventative measures brought on by regional pressures such as fire, frost and disease. Where, more resources were required to prevent these issues from spreading within a region, thus disproportionately effecting some vineyards compared to others locally. This type of maintenance is not well captured especially when considering that some regions, those in warmer areas are not as prone to disease as cooler climates and could potentially have lower operating costs per hectare. This could create a discrepancy in vineyards that utilise preventative measures in wetter regions, as opposed to those who do not, and thus expend less fuel and energy but risk disease. When reviewing the differences between regions it is important to consider that vineyards in Hot Very Dry areas can be hundreds of times the size of those in other regions. It is interesting that while area, although significantly correlated to the ratio of yield to area, was still lower than water and about the same as emissions. This points to economies of scale playing a role but still being only one consideration alongside the potential resources that can be used. The negative trend between size and average sales price could also be a side effect of mass supply verse demand, especially when looking at the level of difference in production of some vineyards (see Table 4). The relationships between yield, value and area are not simply about efficiently producing the most grapes; sales price and by association grape quality, are integral to the profitability, and this is strongly linked to resource-use and thus the longevity and sustainability of a vineyard.
